Subjective Experience of Demands and Resources across O*NET Job Elements

### 2024-07-26 Submission.Rmd
Final Paper Read-through

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes. To illuminate these questions, we consult the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich source of information about occupational requirements (i.e., work activities and context). We retain O\*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

@@

@cavanaugh2000empirical proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Both are considered stressors [e.g., @cavanaugh2000empirical]. Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge]. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].

@@

The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical]. Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).

@lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. demands appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Even @pindek2024dynamic notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do @horan2020review. In fact, although much of our research on job demands based on a priori classifications [@searle2015merits], we contend that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

@horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources. In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p. 3). They go on to suggest future research continue to move away from *a priori* classifications of demands, as doing so can be problematic for theoretical and empirical reasons. Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time [e.g., @searle2015merits].

As such, the first question we ask is whether people distinguish between resources, challenges, and  hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource). Evidence suggests the employees do, in fact, differentiate between challenge and hindrance demands [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending], at least. For example, @bakker2013weekly found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand. @webster2011extending approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees. We aim to both replicate the above findings and extend them to include resources.

@@

The second set of predictions focuses on associations with work-relevant outcomes frequently studied across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical]. Here, we specifically explore appraisals of O\*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout. As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes. See Figure \@ref(fig:ourmodel) for proposed associations.

@@

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].

The findings regarding demands are more complex, presumably because the way challenge vs. hindrance appraisal influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and work meaningful [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example. Challenge appraisals have been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical].

Hindrance demands (appraisals) are largely related to outcomes as the job demands-resources model predicts. When a demand was appraised as a hindrance – it was negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction, [@cavanaugh2000empirical]. @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential]]. Interestingly, both challenges and hindrances have been shown to positively predict strain [(Abbas & Raja, 2019]@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions:

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job]. Bakker and colleagues (2005) were the first to report empirical evidence to support the idea job resources could potentially buffer the negative impact of job demands on stress reactions like burnout. @bakker2005job explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, @xanthopoulou2007job also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows:

>>>>

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands [@webster2011extending] or that appraisals may change over time [@rosen2020challenges]. Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we utilize the [O\*Net database](https://www.onetcenter.org/content.html), which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

@@

@cavanaugh2000empirical proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from @lazarus1984stress's perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between *two forms* of demands -- *challenges* and *hindrances*. Both are considered stressors/demands [e.g., @cavanaugh2000empirical]. Challenge demands promote mastery, personal growth, and future gains – these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility [@lepine2022challenge]. Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity [@lepine2022challenge].

@@

The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes [e.g., @cavanaugh2000empirical]. Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, @lepine2005meta regarding performance and @crawford2010linking regarding engagement).

@lepine2022challenge explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Demands appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions [@lepine2022challenge].

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. @pindek2024dynamic notes this limitation of *a priori* classification of characteristics as demands, challenges, or hindrances, as do @horan2020review. In fact, although much of our research on job demands based on *a priori* classifications [@searle2015merits], the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

Aligned with this dynamic perspective on the experience of work, @horan2020review and @lepine2022challenge specifically call out the need for additional research to incorporate the appraisal process described by @lazarus1984stress into the challenge-hindrance stressor framework. In fact, @horan2020review state that “…stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees” (p. 3). They go on to suggest future research continue to move away from *a priori* classifications of demands, as doing so can be problematic for theoretical and empirical reasons. Theoretically, *a priori* classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time [e.g., @searle2015merits].

Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and  hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource). Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands [e.g., @bakker2013weekly; @gerich2017relevance; @webster2011extending]. For example, @bakker2013weekly found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge. @webster2011extending approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees. We aim to both replicate the above findings and extend them to include resources.

@@

The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- [@bakker2017job] and challenge-hindrance stressor-frameworks [@cavanaugh2000empirical]. Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance [e.g., @lepine2005meta]. We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. See Figure \@ref(fig:ourmodel) for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development [e.g., @bakker2014job; @bakker2017job], and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, @hakanen2008job found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, @bakker2007job found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement [e.g., @schaufeli2017applying].

@@

The findings regarding demands are more complex, presumably because the way challenge vs. hindrance appraisals influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work [@chen2021daily], engagement [@crawford2010linking], and strain and turnover intentions [e.g., @abbas2019challenge], for example. Challenge appraisals have been negatively associated with job search behaviors [e.g., @cavanaugh2000empirical].

Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress. When a demand is appraised as a hindrance – it is negatively associated with motivational resources [@kim2020thriving], engagement [@crawford2010linking], job search behaviors and job satisfaction [@cavanaugh2000empirical]. @chen2021daily found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands [@podsakoff2007differential]]. Interestingly, both challenges and hindrances have been shown to positively predict strain [(Abbas & Raja, 2019]@abbas2019challenge; @lepine2005meta; @podsakoff2007differential; @webster2010toward], which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions [see Figure \@ref(fig:ourmodel)]:

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain [e.g., @bakker2005job] and burnout [e.g., @xanthopoulou2007job]. Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout. @bakker2005job explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, @xanthopoulou2007job also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows [see Figure \@ref(fig:ourmodel)]:

### 2024-07-26 Submission.tex
Final Paper Read-through

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) whether subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and outcomes. To illuminate these questions, we consult the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich source of information about occupational requirements (i.e., work activities and context). We retain O*Net terminology of working condition elements throughout this paper (e.g., personal, contextual, or task-related conditions or elements of one's work).

@@

Cavanaugh et al. (2000) proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Both are considered stressors (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility (M. A. LePine, 2022). Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity (M. A. LePine, 2022).

The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000). Meta-analytic explorations of this the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J. A. LePine et al. (2005) regarding performance and Crawford et al. (2010) regarding engagement).

M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Of note is that this energy may be depleted eventually, leading to strain. demands appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which in contrast, negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022).

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Even Pindek et al. (2024) notes this limitation of a priori classification of characteristics as demands, challenges, or hindrances, as do Horan et al. (2020). In fact, although much of our research on job demands based on a priori classifications (Searle \& Auton, 2015), we contend that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

Horan et al. (2020) and M. A. LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework, which aligns with other calls to capture subjective ratings of demands and resources. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3). They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons. Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).

As such, the first question we ask is whether people distinguish between resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource). Evidence suggests the employees do, in fact, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011), at least. For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance demand, and emotional demands as more of a challenge demand. Webster et al. (2011) approached this question with three common workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance demand, they could also simultaneously be perceived as being both a challenge and hindrance demand to different degrees. We aim to both replicate the above findings and extend them to include resources.

@@

The second set of predictions focuses on associations with work-relevant outcomes frequently studied across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000). Here, we specifically explore appraisals of O*Net-derived work characteristics as resources, challenges, and/or hindrances in association with engagement, strain and burnout. As argued above, appraisals are predicted to be associated with different forms of coping, and subsequently, outcomes. See Figure \ref{fig:ourmodel} for proposed associations.

@@

Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J. A. LePine et al., 2005). We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, Hakanen et al. (2008) found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).

The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisal influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and work meaningful (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example. Challenge appraisals have been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).

Hindrance demands (appraisals) are largely related to outcomes as the job demands-resources model predicts. When a demand was appraised as a hindrance -- it was negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction, (Cavanaugh et al., 2000). Chen et al. (2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007){]}. Interestingly, both challenges and hindrances have been shown to positively predict strain ((Abbas \& Raja, 2019 Abbas \& Raja, 2019; J. A. LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions:

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007). Bakker and colleagues (2005) were the first to report empirical evidence to support the idea job resources could potentially buffer the negative impact of job demands on stress reactions like burnout. Bakker et al. (2005) explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, Xanthopoulou et al. (2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows:

>>>>

While we have accumulated a vast literature on how job demands and resources relate to and influence key organizational outcomes, recent work has called into question some of our basic assumptions regarding the experience of demands in particular. We build on the work of a small, but growing number of researchers who argue that work elements may be appraised simultaneously as resources and demands (Webster et al., 2011) or that appraisals may change over time (Rosen et al., 2020). Our primary aims explore whether: 1) variability exists in subjective ratings of job characteristics with respect to how much they serve as resources and demands, 2) some characteristics are more likely than others to vary across demand and resource, 3) subjective appraisals are differentially related to positive and negative outcomes, and lastly, 4) if resources buffer the relationships between demands (challenge and hindrance) and negative work outcomes. As an additional contribution, we utilize the \href{https://www.onetcenter.org/content.html}{O*Net database}, which provides a rich and generalizable source of information about occupational requirements (i.e., work activities and context).

@@

Cavanaugh et al. (2000) proposed the idea that not all demands are equal with her challenge-hindrance stressor framework, which draws from Lazarus and Folkman (1984)'s perspectives on stress and coping. The challenge-hindrance stressor framework distinguishes between \emph{two forms} of demands -- \emph{challenges} and \emph{hindrances}. Both are considered stressors/demands (e.g., Cavanaugh et al., 2000). Challenge demands promote mastery, personal growth, and future gains -- these demands should lead to coping strategies that facilitate achievement. Work characteristics consistent with this definition, for example, include time pressure and responsibility (M. A. LePine, 2022). Hindrance demands, in contrast, inhibit growth, learning and goal achievement. Example hindrance demands in a work context include role conflict and role ambiguity (M. A. LePine, 2022).

The original work on this topic suggests that challenge demands are typically associated with positive outcomes and hindrance demands are associated with negative outcomes (e.g., Cavanaugh et al., 2000). Meta-analytic explorations of the challenge-hindrance stressor framework have generally been supportive of the framework's propositions (see, for example, J. A. LePine et al. (2005) regarding performance and Crawford et al. (2010) regarding engagement).

M. A. LePine (2022) explain the mechanisms by which demands are related to performance and wellbeing outcomes. First, demands appraised as challenges typically result in a more positive appraisal, and engagement is likely to happen as a result. Engagement, in turn, is positively related to motivation, performance, growth, and wellbeing. Demands appraised as hindrances elicit a different process. Disengagement is likely to result from a hindrance appraisal, which then negatively impacts motivation, performance, growth and wellbeing. This happens because resources are depleted via frustrations and other affectively negative reactions (M. A. LePine, 2022).

@@

Interestingly, much of our existing knowledge regarding the way these relationships between resources/demands and outcomes (e.g., stress, engagement) function is grounded in the assumption that certain job characteristics can generally be considered to be (positive) resources while others can be considered demands. Pindek et al. (2024) notes this limitation of \emph{a priori} classification of characteristics as demands, challenges, or hindrances, as do Horan et al. (2020). In fact, although much of our research on job demands based on \emph{a priori} classifications (Searle \& Auton, 2015), the recent literature suggests that the classification of a work characteristic as a demand or resource is largely subjective by nature (e.g., an employee could most certainly perceive public speaking as a resource or as a demand).

Aligned with this dynamic perspective on the experience of work, Horan et al. (2020) and M. A. LePine (2022) specifically call out the need for additional research to incorporate the appraisal process described by Lazarus and Folkman (1984) into the challenge-hindrance stressor framework. In fact, Horan et al. (2020) state that ``\ldots stressors are only challenge or hindrance demands to the extent that they are perceived as such by employees'' (p.~3). They go on to suggest future research continue to move away from \emph{a priori} classifications of demands, as doing so can be problematic for theoretical and empirical reasons. Theoretically, \emph{a priori} classifications run counter to the original transactional theory of stress on which the challenge-hindrance stressor framework was based for which appraisals are a central component. Empirically, as shown above, we have some evidence suggesting people can appraise a work characteristic as both a hindrance and challenge at the same time (e.g., Searle \& Auton, 2015).

Given the above, the first question we ask is whether people exclusively categorize resources, challenges, and hindrances, and whether a job characteristics might even be considered simultaneously as more than one of these (e.g., both a challenge and a resource). Evidence suggests that employees do, at least, differentiate between challenge and hindrance demands (e.g., Bakker \& Sanz-Vergel, 2013; Gerich, 2017; Webster et al., 2011). For example, Bakker and Sanz-Vergel (2013) found that work pressure was perceived as a hindrance, and emotional demands as more of a challenge. Webster et al. (2011) approached this question with three commonly implicated workplace demands: workload, role ambiguity, and role conflict. They found while that each could be appraised primarily as a challenge or hindrance, they could also simultaneously be perceived as being both a challenge and hindrance to different degrees. We aim to both replicate the above findings and extend them to include resources.

@@

The second set of predictions focus on associations with theory-relevant outcomes across via job demands-resources- (Bakker \& Demerouti, 2017) and challenge-hindrance stressor-frameworks (Cavanaugh et al., 2000). Both the job demands-resources model and the challenge-hindrance stressor framework have been associated with a wide variety of organizational outcomes ranging from affective variables like job satisfaction, to motivation commitment, and performance (e.g., J. A. LePine et al., 2005). We provide only a sampling of associated outcome examples here for context but note that the current project will focus on three outcomes: engagement, strain, and burnout. See Figure \ref{fig:ourmodel} for proposed associations. Resources by definition include aspects of the job that may help an employee achieve work goals, reduce job demands, or promote personal growth and development (e.g., Bakker \& Demerouti, 2014, 2017), and empirical work suggests that they are associated with positive outcomes. Relevant to the current study, for example, Hakanen et al. (2008) found job resources influenced future work engagement. Moreover, in a sample of teachers and dentists, Bakker et al. (2007) found that resources were most predictive of engagement when job demands were especially high. Meta analyses have also concluded that there is a positive association with a variety of resource categories and engagement (e.g., Schaufeli, 2017).

@@

The findings regarding demands are more complex, presumably because the way challenge vs.~hindrance appraisals influence coping strategies. Appraising a demand as a challenge has been positively associated with sources of motivation (i.e., sense of self-worth and meaningful work (Chen et al., 2021), engagement (Crawford et al., 2010), and strain and turnover intentions (e.g., Abbas \& Raja, 2019), for example. Challenge appraisals have been negatively associated with job search behaviors (e.g., Cavanaugh et al., 2000).

Hindrance demands (appraisals) have been found to be related to job demands-resources model outcomes such as decreased motivation and increased stress. When a demand is appraised as a hindrance -- it is negatively associated with motivational resources (Kim \& Beehr, 2020), engagement (Crawford et al., 2010), job search behaviors and job satisfaction (Cavanaugh et al., 2000). Chen et al. (2021) found that daily hindrance demands were negatively associated with cognitive wellbeing and work family enrichment. Further, turnover intentions, turnover and withdrawal behaviors are negatively related to hindrance demands (Podsakoff et al., 2007){]}. Interestingly, both challenges and hindrances have been shown to positively predict strain ((Abbas \& Raja, 2019 Abbas \& Raja, 2019; J. A. LePine et al., 2005; Podsakoff et al., 2007; Webster et al., 2010), which further highlights the complex association between appraisals and subsequent outcomes. Given the differential relationships described above, we make the following predictions {[}see Figure \ref{fig:ourmodel}{]}:

@@

In addition to the these direct relationships, we aim to extend work suggesting that resources can act as a buffer between job demands and strain (e.g., Bakker et al., 2005) and burnout (e.g., Xanthopoulou et al., 2007). Bakker and colleagues (2005) were the first to report empirical evidence to support the idea that job resources could potentially buffer the negative impact of job demands on distal outcomes like burnout. Bakker et al. (2005) explored the interaction between 4 demands (e.g., work overload, physical demands) and 4 resources (e.g., social support, feedback) and three dimensions of burnout (exhaustion, cynicism, and professional efficacy), and found some support for the prediction that high demands with low resources predicted greater levels of cynicism and exhaustion among employees in higher education. Similarly, Xanthopoulou et al. (2007) also found some support for this interaction (high demands + low resources leads to greater burnout) among home healthcare employees. They concluded that a variety of resources, including autonomy, social support, performance feedback, and opportunities for professional development buttered the connection between demands (i.e., patient harassment, workload, physical and emotional demands) and burnout. We extend the established job demands-resources model buffer proposition to both challenge and hindrance demands as follows {[}see Figure \ref{fig:ourmodel}{]}:
